\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[amsthm]{ntheorem} %amsthm but also no newline in lists!
\usepackage[a4paper,margin=2.5cm]{geometry} %greater control over layout
\usepackage{tikz, pgf, pgfplots} %allows tikzpictures
\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
\usepackage{url} %urls easy
\usepackage[shortlabels]{enumitem} %allows greater customisability of enum
\usepackage{textcomp} %gets rid of not defining \perthousand and \micro somehow
\usepackage{gensymb} %symbol package
\usepackage{sectsty}
\usepackage{tabto} %absolute/relative horizontal jumps in text
\usepackage{perpage} %footnote counter resets each page
\usepackage[symbol]{footmisc} %use symbols instead of numbers for footnotes
\usepackage{float} %allows "H" parameter for images
\usepackage{soul} %strikethrough text available

\begin{document}
	\pagenumbering{gobble}
		\noindent \Large\textbf{Mathematical Olympiads Discord Server}
		\vspace{5pt}\\
		\noindent \huge\textbf{2019 June Advanced Contest}\\
		\noindent \makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
			
	\normalsize
	
	\begin{flushright}
	\textit{Time: 4 hours} \hfill \textit{Each problem is worth 7 points}
	\end{flushright}
	
	\noindent \textit{Calculators and protractors are not allowed. Do not write your name on your working. At the end of the contest, please scan your solutions and working and send them to }\texttt{Tony Wang\#6285}\textit{ via direct message. Do not discuss the contents of this paper outside the text channel }\texttt{\#finished- contestants}\textit{ and the voice channel }\texttt{Post-Contest Banter}\textit{ until notified by staff.}
	
	\paragraph{Problem 1.} Let \(n\) be a given positive integer. Find the minimum \(m\) such that for all real sequences \(x_1, x_2, \dots, x_n\) there exists a real number \(y\) such that \[\langle y - x_1 \rangle + \langle y - x_2 \rangle + \dots + \langle y - x_n \rangle \leq m,\] where \(\langle x \rangle = x - \lfloor x \rfloor\) is the difference between \(x\) and the greatest integer less than or equal to \(x\).

	\paragraph{Problem 2.} Sharky has a collection of \(2^n\) strips of \(n \times 1\) strips of paper, with each strip divided into \(n\) unit squares. Each square on a strip is coloured black or white such that every strip is unique. Find the smallest \(m\) such that for any \(m\) strips, Sharky can choose \(n\) of these strips and arrange them (without flipping any of the strips) into a \(n \times n\) square grid with the property that a main diagonal is monochromatic.

	\paragraph{Problem 3.} Let \(ABC\) be a triangle with circumcentre \(O\), and let \(P\) be a point on \(BC\) distinct from \(B\) and \(C\). Construct \(X\) and \(Y\) on \(AB\) and \(AC\) respectively such that \(XB = XP\) and \(YP = YC\). Prove that \(AXOY\) is cyclic.

	\paragraph{Problem 4.} Prove that for all Pythagorean triples \(A\) and \(B\) there exists a finite sequence of Pythagorean triples starting with \(A\) and ending with \(B\) such that any two consecutive triples share at least one number.
	
	(A \emph{Pythagorean triple} is a triple of positive integers \((a, b, c)\) such that \(a\), \(b\), and \(c\) are the side lengths of a right-angled triangle.)
	
	\vfill
	
	\noindent \makebox[\linewidth]{\rule{\textwidth}{0.4pt}}	
	
	\noindent \textit{Mathematical Olympiads Discord Server Invite Link:} \texttt{https://discord.gg/94UnnAG}
		
		
		
		
	
	
\end{document}



















